### 2018-04-23 Paper/jaccardbaetica.tex
add new changes bib

Here, therefore, this study propose an approach to explore the effect of Baetican olive oil production by estimating of similarity index (COPIADO CAMBIAR). The assumption of this analysis is that closer workshops concentrate similar amphoric stamps in a specific area than the farthest workshops. By contrast, if we found similar amphoric stamps in different areas between workshops then the correlation between spatial distance would not be valued.

@@

The chronology in the workshops is widely diverse from the first to the third centuries AD (CITAR). Some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. This could be due to two reasons. First, most of workshops were partially excavated and focused on archaeological surveys in order to collect the maximum stamps as possible. They presented a long chronology. Second, this amphora type was produced during almost three centuries with apparently few changes (PODRÍA CITARME AQUÍ MUAHA)

@@

From the database, we collected the following information: a) the site where it was found and b) the stamp code. We also created a new column with the area where stamps were found (decir berni). Those areas, known as \textit{conventus}, were administrative centers for territorial organization in the Roman Empire (CITAR). Dressel 20 stamps were found in three different \textit{conventus}: Hispalis (currently Seville), Corduba (currently C\'ordoba) and Astigi (currently Écija, Sevilla) \citep{rodriguez_economioleicola_1977,chic_datos_2001,berni_millet_epigrafianforica_2008} .

The distribution of amphora stamps in different conventus can be seen in Fig. \ref{frequency}. The majority of stamps found are concentrated in Hispalis with 574 stamps while Corduba and Astigi with 267 and 146 stamps respectively. Mostly workshops show a homogeneity on frequency of stamps except La Catria and Arva (both show 29 different stamps) that show a big amount of different stamps.  QUIZAS HABLAR DE LA IMPORTANCIA DE LA CATRIA Y ARVA

@@

The correlation coefficients range from a minimum to a maximum. The dendrogram shown in Fig. 2 \ref{dendro} was obtained with Morisita-Horn index. This dendrogram suggests that amphora workshops used different stamps for their prodution system. Accordingly only few closer workshops show a similarity on the stamps while most of them seem to display different stamps roles.

>>>>

Here, therefore, this study proposes an approach to explore the effect of Baetican olive oil production by estimating of similarity index (COPIADO CAMBIAR). The assumption of this analysis is that closer workshops concentrate similar amphoric stamps in a specific area than the farthest workshops. By contrast, if we found similar amphoric stamps in different areas between workshops then the correlation between spatial distance would not be valued.

@@

The chronology in the workshops is widely diverse from the first to the third centuries AD (CITAR). Some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. This could be due to two reasons. First, most of workshops were partially excavated and focused on archaeological surveys in order to collect the maximum stamps as possible. Second, this amphora type was produced during almost three centuries with apparently few changes so they presented a long chronology. (PODRÍA CITARME AQUÍ MUAHA)

@@

From the database, we collected the site where it was found and the stamp code. We also created a new column with the area where stamps were found (decir berni). Those areas, known as \textit{conventus}, were administrative centers for territorial organization in the Roman Empire (CITAR). Dressel 20 stamps were found in three different \textit{conventus}: \textit{Hispalis} (currently Seville), \textit{Corduba} (currently C\'ordoba) and \textit{Astigi} (currently Écija, Sevilla) \citep{rodriguez_economioleicola_1977,chic_datos_2001,berni_millet_epigrafianforica_2008} .

The distribution of amphora stamps in different conventus can be seen in Fig. \ref{frequency}. The majority of stamps found are concentrated in \textit{Hispalis} with 574 stamps while \textit{Corduba} and \textit{Astigi} with 267 and 146 stamps, respectively. Mostly workshops show a homogeneity on frequency of stamps except La Catria and Arva (both show 29 different stamps) that show a big amount of different stamps. According to some researchers, those workshops became in one of the most important centres of amphora production (CITAR) although it could have been intensely prospected. \citep{arva_1997}

@@

The correlation coefficients range from a minimum to a maximum. The dendrogram shown in Fig. \ref{dendro} was obtained with Morisita-Horn index. This dendrogram suggests that amphora workshops used different stamps for their prodution system. Accordingly only few closer workshops show a similarity on the stamps while most of them seem to display different stamps roles.
